On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-24 Manuscript/manuscript.tex
New CIs

@@

>>>>

\paragraph{Centered Bootstrap Percentile CI}
The procedure for constructing a Centered Bootstrap Percentile CI based on standard bootstrap is
described in \citet{singh2008bootstrap}.
The $(1 - \alpha)$ Centered Bootstrap Percentile CI is
\[
(2\hat{\theta}_{n} - \hat\theta_{n, 1 - \alpha/2}^{(b)}, \quad
2\hat{\theta}_{n} - \hat\theta_{n, \alpha/2}^{(b)})).
\]
This CI is necessarily centered around the point estimator $\hat\theta_n$ and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

\paragraph{Bias Corrected Bootstrap CI}
The procedure for constructing a Bias Corrected Bootstrap CI based on standard bootstrap is
described in \citet{carpenter2000bootstrap}.
Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
For a $1 - \alpha$ CI, let
\[
\alpha_1 = \Phi(2b - z_{\alpha/2}).
\]
\[
\alpha_2 = \Phi(2b - z_{1 - \alpha/2}).
\]
A $(1 - \alpha) BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
